The Cluster Difference Imaging Photometric Survey (CDIPS). I. Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-01 paper/ms.tex
update paper

To assign unique cluster names, we adopted the name matched against
\citet{Kharchenko_et_al_2013} whenever possible, following the
procedure described in Appendix~\ref{appendix:uniquenames}.  For
moving groups not identified in \citet{Kharchenko_et_al_2013}, we
adopted the constellation-based naming convention from
\citet{gagne_banyan_XI_2018}.  Otherwise, we used the name reported by
the original catalog.  This process reduced 16,425 name permutations
down to 3,216 unique cluster names.  Though we have made every effort
to avoid duplicates, a small number may remain in this column, so we
advise inspection of the \texttt{cluster} and \texttt{reference}
columns rather than the \texttt{unique_cluster_name} column when
analyzing individual objects of interest.  Nonetheless, 87.7\% of the
$\sim$million unique target stars are matched to clusters within
\citet{Kharchenko_et_al_2013}, and 88.8\% are assigned a cluster name.
The remainder are mostly the young stars from \citet{zari_3d_2018}.

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{ctoi_quilt.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    {\bf 12 of the \numberpcs candidate transiting planets identified
    in this work.} 
    Models are fit as described in \S~\ref{subsec:ctois}.
    The full set of model parameters are in Table~XXX and on
    exofop-TESS.
	\label{fig:ctoi_quilt}
	}
\end{figure*}

@@

In assigning a single unique cluster name to each star, we matched
against the \citet{Kharchenko_et_al_2013} name whenever possible,
since this was the largest available catalog, and it also included
homogeneous age determinations for many of the clusters.
To find the matching name, in order of precedence we
\begin{enumerate}[(i)]
  \item checked for direct string matches from
    \citet{Kharchenko_et_al_2013} clusters with determined parameters;
  \item checked whether the SIMBAD online name resolving service had
    any direct string matches against \citet{Kharchenko_et_al_2013}
    clusters with determined parameters;
  \item checked for string matches in the full
    \citet{Kharchenko_et_al_2013} index (including clusters without
    determined parameters);
  \item searched for spatial matches between each star and cluster
    centers from \citet{Kharchenko_et_al_2013} within 10 arcminutes.
    In cases with multiple cluster matches, we ignored candidate
    matches to avoid assigning incorrect names;
  \item checked the WEBDA double name
    list\footnote{\url{https://webda.physics.muni.cz/double_names.html}},
    and repeated (i)-(iv).
\end{enumerate}

A few edge-cases, including for instance sub-clusters within larger
star-forming complexes like in Sco-Cen or Collinder~33, were 
manually resolved to the extent feasible \citep[][give
detailed pictures of the complex morphologies that frequently arise in
very young star-forming
regions]{rizzuto_multidimensional_2011,saurin_isolating_2015}.

>>>>

To assign unique cluster names, we adopted the name matched against
\citet{Kharchenko_et_al_2013} whenever possible, following the
procedure described in Appendix~\ref{appendix:uniquenames}.  For
moving groups not identified in \citet{Kharchenko_et_al_2013}, we used
the constellation-based naming convention from
\citet{gagne_banyan_XI_2018}.  Otherwise, we used the name reported by
the original catalog claiming membership.  This process reduced 16,425
name permutations down to 3,216 unique cluster names.  Though we have
made every effort to avoid duplicates, a small number may remain, so we
advise inspection of the \texttt{cluster} column
as well as the references given in the
\texttt{reference} column rather than using the
\texttt{unique\_cluster\_name} column to analyze individual objects
of interest.  Nonetheless, 87.7\% of the $\sim$million unique target
stars are matched to clusters within \citet{Kharchenko_et_al_2013},
and 88.8\% are assigned a cluster name.  The remainder are mostly the
young stars from \citet{zari_3d_2018}.

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{tlsresult_sector6.png}%{ctoi_quilt.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    {\bf 12 of the \numberpcs candidate transiting planets identified
    in this work.} 
    Models are fit as described in \S~\ref{subsec:ctois}.
    The full set of model parameters are in Table~XXX and on
    exofop-TESS.
	\label{fig:ctoi_quilt}
	}
\end{figure*}

@@

In assigning a single unique cluster name to each star, we matched
against the \citet{Kharchenko_et_al_2013} name whenever possible,
since this was the largest available catalog, and it also included
homogeneous age determinations for many of the clusters.
To find the matching name, in order of precedence we
\begin{enumerate}
  \item Checked for direct string matches from
    \citet{Kharchenko_et_al_2013} clusters with determined parameters;
  \item Checked whether the SIMBAD online name resolving service \citep{wenger_simbad_2000} had
    any direct string matches against \citet{Kharchenko_et_al_2013}
    clusters with determined parameters;
  \item Checked for string matches in the full
    \citet{Kharchenko_et_al_2013} index (including clusters without
    determined parameters);
  \item Searched for spatial matches between each star and cluster
    centers from \citet{Kharchenko_et_al_2013} within 10 arcminutes.
    In cases with multiple cluster matches, we ignored candidate
    matches to avoid assigning incorrect names;
  \item Checked the WEBDA double name
    list\footnote{\url{https://webda.physics.muni.cz/double_names.html}},
    and repeated Steps 1-4 with any matches.
\end{enumerate}

A few edge-cases, including for instance sub-clusters  larger
star-forming complexes like in Sco-Cen or Collinder~33, were 
manually resolved to the extent feasible (\citealt{rizzuto_multidimensional_2011}
and \citealt{saurin_isolating_2015} give
detailed pictures of the complex morphologies that frequently arise in
young star-forming regions).
